---
Script name: 3D_coldwater_patch.qmd
Author: A. Y. Baynes
Contact: abaynes@umass.edu

Objective: Show how coldwater patch size
Data source: Flume project
Output: 
- 3D scatterplot figures of coldwater patch tempeature
- 3D isosurface figures of coldwater patch temperature
- Volume under the isosurface (volume of coldwater patch)

Table of contents:
 3D Coldwater Patch
 0. Load libraries and data
 1. 2D coldwater patch, run
 2. 2D coldwater patch, run, barrier
 3. 3D coldwater patch, Run1
 4. 3D CWP, Pool2
 5. All seeps on 4.0-4.5 L/min
 6. Increase seep flow rate 8.8L/min
 7. Increase seep flow rate 10.6L/min
 8. Increase seep flow rate 11.7L/min
---

# 3D Coldwater Patch {.unnumbered}

## 0. Load Libraries and data

```{r setup, include=FALSE}
rm(list = ls())

library(sf)
library(ggplot2)
require(ggspatial)
library(tidyr)
library(dplyr)
library(plotly)
library(grid) #to add arrow in plot
library(here)
here()
```

## 1. 2D coldwater patch, run

2026-02-04

### Load Data

```{r}
grid <- read.csv(here("Data","Temperature_probe","grid_20260204.csv"))
str(grid)
```

### Create grids

```{r}
# Plot
plot1 <- ggplot(data = grid, aes(x = x, y = y, fill = Temperature.C)) +
  geom_tile(color = "white", linewidth = 0.5) +
  scale_x_continuous(position = "top") +  # Move x-axis to the top
  scale_y_reverse() +   # Reverse the y-axis
  coord_fixed(ratio = 60 / 100) +
  ggtitle("Coldwater patch temperature (°C) in run") +
  xlab("Measure every 10 cm") +  # Rename the x-axis
  ylab("Measure every 20 cm") +
  theme_bw()
plot1

out_path = here("Figures")
ggsave("cwp_run_20260204.png",
       plot = plot1,
       path = out_path,
       width = 5,
       height = 5,
       dpi = 300)
```

## 2. 2D coldwater patch, run, barrier

2026-02-10

### Load Data

```{r}
grid <- read.csv(here("Data","Temperature_probe","grid_barrier_20260210.csv"))
str(grid)
```

### Create grids

```{r}
# Plot
plot1 <- ggplot(data = grid, aes(x = x, y = y, fill = Temperature.C)) +
  geom_tile(color = "white", linewidth = 0.5) +
  scale_x_continuous(position = "top") +  # Move x-axis to the top
  scale_y_reverse() +   # Reverse the y-axis
  coord_fixed(ratio = 80 / 100) +
  ggtitle("Coldwater patch temperature (°C) in run") +
  xlab("Measure every 10 cm") +  # Rename the x-axis
  ylab("Measure every 10 cm") +
  theme_bw()
plot1

out_path = here("Figures")
ggsave("cwp_run_barrier_20260210.png",
       plot = plot1,
       path = out_path,
       width = 7,
       height = 5,
       dpi = 300)
```

## 3. 3D CWP, Run 1

```{r}
pts_2D <- read.csv(here("Data","Thermocouple","Point_measurement","2D_20260217_run1.csv"))
pts_3D <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260218_run1.csv"))
pts_3D_barrier <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260218_run1_barrier.csv"))
pts_3D_barrier2 <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260218_run1_barrier2.csv"))

str(pts_3D_barrier2)
```

### 2D CWP cross section with barrier

```{r}
library(plotly)

plot_ly(
  pts_2D,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_2D$cross_section), min(pts_2D$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )

```

### 3D CWP

```{r}
plot_ly(
  pts_3D,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D$cross_section), min(pts_3D$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )

```

**3D CWP isosurface**

```{r}
plot_ly(
  pts_3D,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 23,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D$cross_section), min(pts_3D$cross_section))  # reverse only x
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )

```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 23

# Volume under isosurface
volume <- pts_3D %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```

### 3D CWP barrier (1 brick)

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**3D CWP barrier isosurface (1 brick)**

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 23,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reverse only x
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D_barrier$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D_barrier$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D_barrier$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 23

# Volume under isosurface
volume <- pts_3D_barrier %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```

### 3D CWP barrier (2 bricks)

```{r}
plot_ly(
  pts_3D_barrier2,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(title = "Cross Section",
                   range = c(max(pts_3D_barrier2$cross_section), min(pts_3D_barrier2$cross_section))),  # reversed
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth"),
      aspectmode = "manual",
      aspectratio = list(x = 1, y = 0.3, z = 1) # compress y axis
    )
  )
```

**3D CWP barrier isosurface (2 bricks)**

```{r}
plot_ly(
  pts_3D_barrier2,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 23,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier2$cross_section), min(pts_3D_barrier2$cross_section))  # reverse only x
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth"),
      aspectmode = "manual",
      aspectratio = list(x = 1, y = 0.3, z = 1)  # compress y axis
    )
  )
```

## 4. 3D CWP, Pool 2

```{r}
pts_3D <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260225_pool2.csv"))
pts_3D_barrier <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260302_pool2_barrier.csv"))

pts_3D <- pts_3D %>%
  filter(!is.na(Temperature))

str(pts_3D)
```

### 3D CWP

Missing 5x40, 40x15, and 15x0x3. Remeasured exact points

```{r}
plot_ly(
  pts_3D,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D$cross_section), min(pts_3D$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )

```

**3D CWP isosurface**

Missing 5x40, 40x15, and 15x0x3. Remeasured exact points

```{r}
plot_ly(
  pts_3D,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D$cross_section), min(pts_3D$cross_section)) ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 22

# Volume under isosurface
volume <- pts_3D %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume

volume
```

### 3D CWP barrier (1 brick)

Brick against the outer wall

Missing 15x20. Estimated exact points

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )

```

**3D CWP barrier isosurface (1 brick)**

Missing 15x20. Estimated exact points

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reverse only x
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )

```

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D_barrier$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D_barrier$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D_barrier$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 22

# Volume under isosurface
volume <- pts_3D_barrier %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume

volume
```

## 5. All seeps on 4.0-4.5L/min

```{r}
pts_3D_barrier <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260303_run2_barrier.csv"))
#pts_3D_barrier <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260303_run2_barrier copy.csv"))
pts_3D_pool <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260305_pool2.csv"))

#str(pts_3D)
```

### 3D CWP Run2 barrier (1 brick)

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**3D CWP Run2 barrier isosurface (1 brick)**

Missing 15x20x6.4

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reverse only x
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D_barrier$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D_barrier$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D_barrier$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 23

# Volume under isosurface
volume <- pts_3D_barrier %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```

**Offset 1 point**

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22.5,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reverse only x
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )

```

### 3D CWP Pool2

```{r}
plot_ly(
  pts_3D_pool,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_pool$cross_section), min(pts_3D_pool$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**3D CWP Pool2 isosurface**

Missing 15x20x6.4

```{r}
plot_ly(
  pts_3D_pool,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_pool$cross_section), min(pts_3D_pool$cross_section))  # reverse only x
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D_pool$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D_pool$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D_pool$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 22

# Volume under isosurface
volume <- pts_3D_pool %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```

## 6. Increase seep flow rate 8.8L/min

```{r}
pts_3D <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260304_run1.csv"))
pts_3D_barrier <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260304_run1_barrier.csv"))

#str(pts_3D)
```

### 3D CWP Run1

```{r}
plot_ly(
  pts_3D,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D$cross_section), min(pts_3D$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**3D CWP Run1 isosurface**

Missing . Remeasured exact points

```{r}
plot_ly(
  pts_3D,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D$cross_section), min(pts_3D$cross_section)) ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 22

# Volume under isosurface
volume <- pts_3D %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```

### 3D CWP Run1 barrier

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**3D CWP Run1 barrier isosurface**

Missing . Remeasured exact points

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section)) ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D_barrier$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D_barrier$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D_barrier$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 22

# Volume under isosurface
volume <- pts_3D_barrier %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```

## 7. Increase seep flow rate 10.6L/min

```{r}
pts_3D_barrier <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260309_run1_barrier.csv"))

#str(pts_3D)
```

### 3D CWP Run1 barrier

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**3D CWP Run1 barrier isosurface**

Missing . Remeasured exact points

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section)) ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D_barrier$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D_barrier$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D_barrier$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 22

# Volume under isosurface
volume <- pts_3D_barrier %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```

## 8. Increase seep flow rate 11.7L/min

```{r}
pts_3D_barrier <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260311_run1_barrier.csv"))
pts_3D_barrier2 <- read.csv(here("Data","Thermocouple","Point_measurement","3D_20260311_run1_barrier2.csv"))

pts_3D_barrier2 <- pts_3D_barrier2 %>%
  filter(!is.na(Temperature))

#str(pts_3D)
```

### 3D CWP Run1 barrier

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**3D CWP Run1 barrier isosurface**

Missing . Remeasured exact points

```{r}
plot_ly(
  pts_3D_barrier,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier$cross_section), min(pts_3D_barrier$cross_section)) ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D_barrier$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D_barrier$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D_barrier$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 22

# Volume under isosurface
volume <- pts_3D_barrier %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```

### 3D CWP Run1 barrier (2bricks)

```{r}
plot_ly(
  pts_3D_barrier2,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  color = ~Temperature,
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 6)
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier2$cross_section), min(pts_3D_barrier2$cross_section))  # reversed
      ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**3D CWP Run1 barrier isosurface**

```{r}
plot_ly(
  pts_3D_barrier2,
  x = ~cross_section,
  y = ~longitudinal,
  z = ~depth,
  value = ~Temperature,
  type = "isosurface",
  isomin = 20,
  isomax = 22,
  surface_count = 2,
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
  )
) %>%
  layout(
    scene = list(
      xaxis = list(
        title = "Cross Section",
        range = c(max(pts_3D_barrier2$cross_section), min(pts_3D_barrier2$cross_section)) ),
      yaxis = list(title = "Longitudinal"),
      zaxis = list(title = "Depth")
    )
  )
```

**Area under isosurface**

```{r}
# Determines voxel volume (size of one unit in cm3)
d_cross_section <- diff(sort(unique(pts_3D_barrier2$cross_section)))[1]
d_longitudinal <- diff(sort(unique(pts_3D_barrier2$longitudinal)))[1]
d_depth <- diff(sort(unique(pts_3D_barrier2$depth)))[1]

voxel_volume <- d_cross_section * d_longitudinal * d_depth

# Set temperature threshold
threshold <- 22

# Volume under isosurface
volume <- pts_3D_barrier2 %>%
  filter(Temperature <= threshold) %>%
  nrow() * voxel_volume
volume
```
